Methods and Results

### 2021-08-24 Methods and Results.Rmd
adding old version

---
title: "Methods and Results"
author: "L Heron"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

@@

@@

q2_1_asymp <- metabin(event.e = Ee_a,
                      n.e = Ne_a,
                      event.c = Ec,
                      n.c = Nc, 
                      data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_a),],
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE)
q2_1_asymp

png(file = 'forest_meta_Q2_1_asymp.png',width=750,height=250)

forest(q2_1_asymp)

@@

#metaanalysis for presymptomatic transmission

q2_1_presymp <- metabin(event.e = Ee_p,
                        n.e = Ne_p,
                        event.c = Ec,
                        n.c = Nc, 
                        data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_p),],
                        studlab = author_1,
                        prediction = TRUE,
                        sm = "RR",
                        method = "MH",
                        MH.exact = TRUE)

q2_1_presymp

png(file = 'forest_meta_Q2_1_presymp.png',width=750,height=190)

forest(q2_1_presymp)

@@

![Figure 2. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_asymp.png)

![Figure 3. Forest plot of secondary attack rate comparing infections in contacts of presymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_presymp.png)

>>>>

---
title: "Methods and Results"
author: "L Heron"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

@@

#create new df with asymp/presymp as subgroups
q2_1_df_a <- asymptomaticQ2_1 %>%
  select("record_id", "author_1", "Ee_a", "Ne_a", "Ec", "Nc", "region", "year") %>%
  rename(Ee = Ee_a,
         Ne = Ne_a) %>%
  filter(!is.na(Ee)) %>%
  mutate(group = "Asymptomatic")
q2_1_df_p <- asymptomaticQ2_1 %>%
  select("record_id", "author_1", "Ee_p", "Ne_p", "Ec", "Nc", "region", "year") %>%
  rename(Ee = Ee_p,
         Ne = Ne_p) %>%
  filter(!is.na(Ee)) %>%
  mutate(group = "Presymptomatic")
#bind rows
q2_1_df <- bind_rows(q2_1_df_a, q2_1_df_p)

@@

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group)
q2_1_asymp

pdf(file = 'forest_meta_Q2_1.pdf', width = 10, height = 6)

forest(q2_1_asymp, overall = FALSE)

@@

##########################################
# supplementary information - by precision
##########################################

q2_1_asymp_precision <- metabin(event.e = Ee,
                                n.e = Ne,
                                event.c = Ec,
                                n.c = Nc, 
                                data = q2_1_df,
                                studlab = author_1,
                                sm = "RR",
                                byvar = group)

pdf(file = 'forest_meta_Q2_1_precision.pdf', width = 10, height = 6)

forest(q2_1_asymp_precision, sortvar = -seTE, overall = FALSE)

@@

![Figure 2. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic and presymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1.pdf)
